### 2018-03-15 paper/5-implementations.tex
Wibbles

\begin{minted}{haskell}
make :: Eq v => Build Applicative (Changed k v, ()) k v
make = withChanged $ topological $ \k dk act -> do
    t <- getStoreTime k
    dt <- mapM getStoreTime dk
    let dirty = any (>= t) dt
    when dirty $
        putStore k =<< act
\end{minted}

@@

\begin{minted}{haskell}
makeDirtyBit :: Eq v => Build Applicative (Changed k v, ()) k v
makeDirtyBit = withChanged $ topological $ \k dk act -> do
    dirty <- getChanged k ||^ anyM getChanged dk
    when dirty $
        putStore k =<< act
\end{minted}

>>>>

\begin{minted}{haskell}
make :: Eq v => Build Applicative (Changed k v, ()) k v
make = withChanged $ topological $ \k dk act -> do
    t <- getStoreTime k
    dt <- mapM getStoreTime dk
    let dirty = any (>= t) dt
    when dirty (putStore k =<< act)
\end{minted}

@@

\begin{minted}{haskell}
makeDirtyBit :: Eq v => Build Applicative (Changed k v, ()) k v
makeDirtyBit = withChanged $ topological $ \k dk act -> do
    dirty <- getChanged k ||^ anyM getChanged dk
    when dirty (putStore k =<< act)
\end{minted}
